Plotting plots and Hotzenplotz

### 2024-11-08 draftdata.Rmd
pushitpushitrestructure

---
title: "draft-data"
author: "Verooo"
date: "2024-11-01"
output: html_document
---

@@

# Data Draft

@@

## DV: Collaboration between scholars

@@

-   Names of scholars manually checked in Dutch Voornamenbank website **(NAME WEBSITE)**

@@

@@

@@

```{=html}
<!-- -->
```
-

>>>>

---
title: "draft-data"
author: "Verooo"
date: "2024-11-01"
output: html_document
bibliography: references.bib
---

@@

# Data

@@

## DV: formation of ties between scholars

-   formation of ties between scholars

-   adjacency-matrix

@@

-   Names of scholars manually checked in Dutch Voornamenbank website of the Meertens Institute (@MeertensInstituut)

@@

-   control variable in this research design

@@

        -    H-index: Hirsch-Index

            -   From Lucan: "The h-index namely measures an author’s prestige by calculating the number of publications that have been cited at least as many times as the total number of their publications. As explained by the creator of the h-index, ” A scientist has index h if h of his or her Np papers have at least h citations each and the other (Np - h) papers have ≤h citations each” (@Hirsch2005) "

        -   i10-index:

@@

```{=html}
<!-- -->
```
-   Code for this was provided by a fellow course mate, namely Lucan Bovens

# Data preparation /Methods

### RSiena

-   definition

    -   "SIENA, shorthand for **Simulation Investigation for Empirical Network Analysis**, is a computer program that carries out the statistical estimation of models for repeated measures of social networks according to the dynamic actor-oriented model of Snijders and van Duijn (1997), Snijders (2001), and Snijders, Steglich, and Schweinberger (2007); also see Steglich, Snijders, and Pearson (2009). A tutorial for these models is in Snijders, van de Bunt, and Steglich (2009). Some examples are presented, e.g., in van de Bunt (1999); van de Bunt, van Duijn, and Snijders (1999); and van Duijn, Zeggelink, Stokman, and Wasseur (2003); and Steglich, Snijders, and West (2006). A website for SIENA is maintained at http://www.stats.ox.ac.uk/\~snijders/siena/ . At this website (‘publications’ tab) you shall also find references to introductions in various other languages.
        This is a provisional manual for SIENA version 4.0, which is also called RSiena. This is a contributed package for the R statistical system which can be downloaded from http://cran.r-project.org. For the operation of R, the reader is referred to the corresponding manual. If desired, SIENA can be operated apparently independently of R, as is explained in Section 2.1.
        RSiena was programmed by Ruth Ripley and Krists Boitmanis, in collaboration with Tom Snijders."

Ripley, Ruth, and Snijders, Tom A.B. 2009. Manual for SIENA version 4.0 (provisional version, July 6, 2009). Oxford: University of Oxford, Department of Statistics; Nuffield College. <http://www.stats.ox.ac.uk/siena/>

Manual reference: @RSiena_manual

Siena package refrence: @RSiena_package

Methods, aka use of RSiena for SNA

-   Jochem Tolsma and Bas Hofstra: [**Methods**](https://jochemtolsma.github.io/SNA-4-Social-Scientists/socionetsm.html) (focusing on RSiena), Chapter 7 of [**Social Network Analysis for Social Scientists**](https://jochemtolsma.github.io/SNA-4-Social-Scientists/) ("SNASS").

    -   reference: \@SNASS

# Data description

### 2024-11-08 revisitwithJochem.Rmd
pushitpushitrestructure

#### soc department

```{r}
# # dependent
# net <- sienaDependent(net_soc_array)

# dependent ?
# nets <- testsoc$nets

@@

  rownames(nets[1,,]) == df_soc_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
  # --> yes, the correct ones!!!

@@

#### polsci department

@@

# DEMO
  str(df_pol_ego_demo, 1)

@@

### gender-soc

@@

# check if it went smoothly 
view(df_soc_ego[c('Naam', 'gender', 'au_id')])

@@

# check if it went smoothly 
view(df_pol_ego[c('Naam', 'gender', 'au_id')])

@@

```{r combine gender set}
df <- test$data # make dataset with all data 
df_ego <- do.call(rbind.data.frame, df$demographics) # dataset with demographic information

@@

df_ego <- df_ego %>% 
            left_join(gender) #dcombininf dataset of gender with the one with demographic information 
```

@@

#put diagonals to zero 
diag(wave1) <- 0
diag(wave2) <- 0
# we want a binary tie (not a weighted tie)
wave1[wave1 > 1] <- 1
wave2[wave2 > 1] <- 1
# put the nets in an array
net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))

gender <- df_ego$gender

#dependent
nets <- sienaDependent(net_array)
#covariate
genderrs <- coCovar(gender)
#define data 
mydata <- sienaDataCreate(nets, genderrs)

@@

#skipped description

@@

myeff <- includeEffects(myeff, egoX, altX, sameX, interaction1 = "genderrs")

#look up which effects to iclude

myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
# undirected: model 6 "additive model", #check manual for this

# estimate
model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
#latter needed for GOF

@@

# H-index webscraping

Credits to Lucan for the code.

```{r h-index, include=FALSE, eval= FALSE}
# Add h-index and i10-index columns to df_ego
df_ego <- df_both_ego %>%
  mutate(h_index = NA_real_, i10_index = NA_real_)

#covariate 
# h_index <- coCovar(df_ego$h_index)
```

# Plotting

```{r}
test_w1 <- igraph::graph_from_adjacency_matrix(
  test$nets[1,,], # first wave of data. 
  # (thus I select the array of networks and take the first matrix)
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL,
  add.rownames = NULL)

@@

plot(test_w1,
vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), #now, I can use actor attributes for plotting.
# here: if gender = 1 (aka man) then red dot, if not then blue 
vertex.label = NA,
edge.width = 0.2,
edge.arrow.size =0.2)

>>>>

#### soc department save

```{r}
soc_nets <- testsoc$nets

@@

  rownames(soc_nets[1,,]) == df_soc_ego$au_id # checking if the author id's are the same as in df_ego in nets dataframe 
  # --> yes, the correct ones!!!

@@

#### polsci department save

@@

# DEMO
  #str(df_pol_ego_demo, 1)

@@

### gender - sociology department

@@

# check if it went smoothly 
# view(df_soc_ego[c('Naam', 'gender', 'au_id')])

@@

# check if it went smoothly 
# view(df_pol_ego[c('Naam', 'gender', 'au_id')])

@@

```{r combine gender set}
df <- test$data # make dataset with all data 
df_ego <- do.call(rbind.data.frame, df$demographics) # data set with demographic information

@@

df_ego <- df_ego %>% 
            left_join(gender) #dcombining data set of gender with the one with demographic information 
```

# H-index 
Credits to Lucan Bovens for the code.

```{r h-index}
# Add h-index and i10-index columns to df_ego
df_ego <- df_ego %>%
  mutate(h_index = NA_real_, i10_index = NA_real_)

@@

#put diagonals to zero 
diag(wave1) <- 0
diag(wave2) <- 0
# we want a binary tie (not a weighted tie)
wave1[wave1 > 1] <- 1
wave2[wave2 > 1] <- 1
```

```{r RSiena2}
# put the nets in an array
net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
#dependent
nets <- sienaDependent(net_array)

#put gender in object 
gender <- df_ego$gender
#covariate
gender_RS <- coCovar(gender) # gender as covariate in Rsiena

#put h-index in object 
h_index <- df_ego$h_index
df_ego$h_index
#covarite 2
h_index_RS <- coCovar(h_index) # h_index as covariate in RSiena

#define data 
mydata <- sienaDataCreate(nets, gender_RS, h_index_RS)

@@

# skipped initial description part

@@

myeff <- includeEffects(myeff, egoX, altX, sameX, interaction1 = "gender_RS")
#include effect of h index later too etc
#look up which effects to iclude

myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
# undirected: model 6 "additive model", #check manual for this
```

```{r RSiena-model estimate}
# estimate the model 
model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
#latter needed for GOF

@@

# Plotting
```{r}
test_w1 <- igraph::graph_from_adjacency_matrix(
  test$nets[1,,], # first wave of data. 
  # (thus I select the array of networks and take the first matrix)
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL,
  add.rownames = NULL)

@@

plot(test_w1,
vertex.color = ifelse(df_ego$gender == 1, "red", "blue"), # now, I can use actor attributes for plotting.
# here: if gender = 1 (aka man) then red dot, if not then blue 
vertex.label = NA,
edge.width = 0.2,
edge.arrow.size =0.2)
